SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-05 scipy-1.0/paper.tex
Add a 'what is SciPy' section to the introduction

Traditionally, a 1.0 release signals that a
library's API has reached a level of maturity and stability
that warrants trusting it inside research pipelines.
The SciPy 1.0 version numbering belies the history of a project
that has become the standard which others follow
and has seen extensive adoption in research and industry.

@@

% scikits
%https://mail.python.org/pipermail/scipy-dev/2006-November/006315.html
%https://mail.python.org/pipermail/scipy-dev/2006-November/006316.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006972.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006835.html

>>>>

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  It is the foundation upon which higher level scientific
libraries, including scikit-learn and scikit-image, are built.

Recently, SciPy released version 1.0, a milestone that traditionally
signals a library's API (Applications Programming Interface) being
mature enough to be be trusted in production pipelines.  The SciPy 1.0
version numbering, however, belies the history of a project that has
become the standard which others follow and has seen extensive
adoption in research and industry.

@@

% scikits

% First scikit (mail moving over from nipy list?)
% https://mail.python.org/pipermail/scipy-dev/2007-March/006805.html

% First scikit development:
% https://mail.python.org/pipermail/scipy-dev/2007-April/006987.html

%https://mail.python.org/pipermail/scipy-dev/2006-November/006315.html
%https://mail.python.org/pipermail/scipy-dev/2006-November/006316.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006972.html
%https://mail.python.org/pipermail/scipy-dev/2007-April/006835.html
